An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-06-16 Article/EconGrowth2-GraphsOnly.Rnw
Now building all graphs. In the Graphs-Only version of the paper, we weren't using the new versions of nestStr and nestStrParen.

<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6, fig.height=8.2, fig.cap="Cobb-Douglas fitted models.">>=
cdFittedData <- filter(fitted_df, model=="cd", nest %in% c("iK+iL", "iK+iL+iQ", "iK+iL+iX", "iK+iL+iU"))
spaghettiPlot(data=cdFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@

% <<CES_lambda_gamma_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models.">>=
% cesCoeffsData <- filter(coeffs_df, model=="ces", nestStr %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
% standardScatterPlot(data=cesCoeffsData, mapping=aes(gamma_coef, lambda), facet_formula=country~nest, alpha=0.05) +
%     scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
%     scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
%     labs(x=expression(gamma), y=expression(lambda))
% @

<<CES_lambda_gamma_graph_kle, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with (kl)e nesting.">>=
cesCoeffsData_kle <- filter(coeffs_df, model=="ces", nestStr %in% c("iK+iL", "iK+iL+iQ", "iK+iL+iX", "iK+iL+iU"))
standardScatterPlot(data=cesCoeffsData_kle, mapping=aes(gamma_coef, lambda), facet_formula=country~nest, alpha=0.05) +
    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
    scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
    labs(x=expression(gamma), y=expression(lambda))
@

<<CES_lambda_gamma_graph_lek, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with (le)k nesting.">>=
cesCoeffsData_lek <- filter(coeffs_df, model=="ces", nestStr %in% c("iK+iL", "iL+iQ+iK", "iL+iX+iK", "iL+iU+iK"))
standardScatterPlot(data=cesCoeffsData_lek, mapping=aes(gamma_coef, lambda), facet_formula=country~nest, alpha=0.05) +
    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
    scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
    labs(x=expression(gamma), y=expression(lambda))
@

<<CES_lambda_gamma_graph_ekl, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with (ek)l nesting.">>=
cesCoeffsData_ekl <- filter(coeffs_df, model=="ces", nestStr %in% c("iK+iL", "iQ+iK+iL", "iX+iK+iL", "iU+iK+iL"))
standardScatterPlot(data=cesCoeffsData_ekl, mapping=aes(gamma_coef, lambda), facet_formula=country~nest, alpha=0.05) +
    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
    scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
    labs(x=expression(gamma), y=expression(lambda))
@

% <<CES_sigma1_delta1_graph, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models.">>=
% standardScatterPlot(data=cesCoeffsData, mapping=aes(delta_1, sigma_1), facet_formula=country~nest, alpha=0.05) +
%     coord_trans(y="sigma") +
%     scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
%     scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
%     labs(x=expression(delta[1]), y=expression(sigma[1]))
% @

<<CES_sigma1_delta1_graph_kle, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with (kl)e nesting.">>=
standardScatterPlot(data=cesCoeffsData_kle, mapping=aes(delta_1, sigma_1), facet_formula=country~nest, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta[1]), y=expression(sigma[1]))
@

<<CES_sigma1_delta1_graph_lek, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with (le)k nesting.">>=
standardScatterPlot(data=cesCoeffsData_lek, mapping=aes(delta_1, sigma_1), facet_formula=country~nest, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta[1]), y=expression(sigma[1]))
@

<<CES_sigma1_delta1_graph_ekl, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with (ek)l nesting.">>=
standardScatterPlot(data=cesCoeffsData_ekl, mapping=aes(delta_1, sigma_1), facet_formula=country~nest, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta[1]), y=expression(sigma[1]))
@

% # <<CES_sigma_delta_graph, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models.">>=
% #  standardScatterPlot(data=subset(cesCoeffsData, nestStr != "iK+iL"),
% #                      mapping=aes(delta, sigma), facet_formula=country~nest, alpha=0.05) +
% #      coord_trans(y="sigma") +
% #      scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
% #      scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
% #      labs(x=expression(delta), y=expression(sigma))
% #  @

<<CES_sigma_delta_graph_kle, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with (kl)e nesting.">>=
standardScatterPlot(data=subset(cesCoeffsData_kle, nestStr != "iK+iL"),
                    mapping=aes(delta, sigma), facet_formula=country~nest, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta), y=expression(sigma))
@

<<CES_sigma_delta_graph_lek, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with (le)k nesting.">>=
standardScatterPlot(data=subset(cesCoeffsData_lek, nestStr != "iK+iL"),
                    mapping=aes(delta, sigma), facet_formula=country~nest, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta), y=expression(sigma))
@

<<CES_sigma_delta_graph_ekl, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with (ek)l nesting.">>=
standardScatterPlot(data=subset(cesCoeffsData_ekl, nestStr != "iK+iL"),
                    mapping=aes(delta, sigma), facet_formula=country~nest, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta), y=expression(sigma))
@

@@

<<CES_ternary_graph_kle, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with (kl)e nesting.">>=
standardTriPlot(data=cesCoeffsData_kle, facet_formula=country~nest)
@

<<CES_ternary_graph_lek, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with (le)k nesting.">>=
standardTriPlot(data=cesCoeffsData_lek, facet_formula=country~nest)
@

<<CES_ternary_graph_ekl, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with (ek)l nesting.">>=
standardTriPlot(data=cesCoeffsData_ekl, facet_formula=country~nest)
@

% <<CES_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models.">>=
% cesFittedData <- filter(fitted_df, model=="ces", nest %in% c("iK+iL", "iK+iL+iQ", "iL+iQ+iK", "iQ+iK+iL"))
% spaghettiPlot(data=cesFittedData, facet_formula=Country~nest, level=spaghettiGraphLevel) +
%     labs(y="Indexed GDP (1980=1 or 1991=1)")
% @

<<CES_Spaghetti_Graph_kle, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with (kl)e nesting.">>=
cesFittedData <- filter(fitted_df, model=="ces", nest %in% c("iK+iL", "iK+iL+iQ", "iK+iL+iX", "iK+iL+iU"))
spaghettiPlot(data=cesFittedData, facet_formula=Country~nest, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@

<<CES_Spaghetti_Graph_lek, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with (le)k nesting.">>=
cesFittedData <- filter(fitted_df, model=="ces", nest %in% c("iK+iL", "iL+iQ+iK", "iL+iX+iK", "iL+iU+iK"))
spaghettiPlot(data=cesFittedData, facet_formula=Country~nest, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@

<<CES_Spaghetti_Graph_ekl, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with (ek)l nesting.">>=
cesFittedData <- filter(fitted_df, model=="ces", nest %in% c("iK+iL", "iQ+iK+iL", "iX+iK+iL", "iU+iK+iL"))
spaghettiPlot(data=cesFittedData, facet_formula=Country~nest, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@

% <<CES_Spaghetti_Graph_CN, fig.pos="H", fig.align='center', fig.width=maxWidth, fig.height=maxHeight, fig.cap="CES fitted models for China with the (kl)e nesting.">>=
% spaghettiPlot(data=subset(cesFittedData, Country=="CN" & nest=="iK+iL+iQ"), level=spaghettiGraphLevel) +
%     labs(y="Indexed GDP (1980 = 1 or 1991 = 1")
% @

% <<LINEXq_Resample_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7, fig.cap="LINEX model (with energy) resampling results.">>=
% linexCoeffsData <- filter(coeffs_df, model=="linex", energy=="q")
% standardScatterPlot(data=linexCoeffsData, aes(a_0, c_t), facet_formula=country~energy, alpha=0.05) +
%     labs(x=expression(a[0]), y=expression(c[t])) +
%      scale_x_continuous(limits=c(-1, 2), breaks=c(-1, 0, 1.0, 2.0)) +
%      scale_y_continuous(limits=c(0, 10), breaks=c(0, 5, 10))
% @

@@

% <<LINEX_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=2, fig.height=7.1, fig.cap="LINEX fitted models.">>=
% linexFittedData <- filter(fitted_df, model=="linex", energy=="q")
% spaghettiPlot(data=linexFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
%     labs(y="Indexed GDP (1980=1 or 1991=1)")
% @

>>>>

<<CD_GDP_Spaghetti_Graph, fig.pos="H", fig.align='center', fig.width=6, fig.height=8.2, fig.cap="Cobb-Douglas fitted models.">>=
cdFittedData <- filter(fitted_df, model=="cd")
spaghettiPlot(data=cdFittedData, facet_formula=Country~energy, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@

<<CES_lambda_gamma_graph_kle, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with (kl)e nesting.">>=
cesCoeffsData_kle <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", "(iK + iL) + (iQ)", "(iK + iL) + (iX)", "(iK + iL) + (iU)"))
standardScatterPlot(data=cesCoeffsData_kle, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
    scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
    labs(x=expression(gamma), y=expression(lambda))
@

<<CES_lambda_gamma_graph_lek, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with (le)k nesting.">>=
cesCoeffsData_lek <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", "(iL + iQ) + (iK)", "(iL + iX) + (iK)", "(iL + iU) + (iK)"))
standardScatterPlot(data=cesCoeffsData_lek, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
    scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
    labs(x=expression(gamma), y=expression(lambda))
@

<<CES_lambda_gamma_graph_ekl, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\lambda$ and $\\gamma$ values for CES resample models with (ek)l nesting.">>=
cesCoeffsData_ekl <- filter(coeffs_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", "(iQ + iK) + (iL)", "(iX + iK) + (iL)", "(iU + iK) + (iL)"))
standardScatterPlot(data=cesCoeffsData_ekl, mapping=aes(gamma_coef, lambda), facet_formula=country~nestStrParen, alpha=0.05) +
    scale_x_continuous(breaks=c(0.9, 1.0, 1.1)) +
    scale_y_continuous(breaks=c(0, 0.025, 0.05, 0.075)) +    
    labs(x=expression(gamma), y=expression(lambda))
@

<<CES_sigma1_delta1_graph_kle, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with (kl)e nesting.">>=
standardScatterPlot(data=cesCoeffsData_kle, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta[1]), y=expression(sigma[1]))
@

<<CES_sigma1_delta1_graph_lek, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with (le)k nesting.">>=
standardScatterPlot(data=cesCoeffsData_lek, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta[1]), y=expression(sigma[1]))
@

<<CES_sigma1_delta1_graph_ekl, fig.pos="H", fig.align='center', fig.width=fourPanelScatterGraphWidth, fig.height=ninePanelScatterGraphHeight, fig.cap="$\\sigma_1$ and $\\delta_1$ values for CES resample models with (ek)l nesting.">>=
standardScatterPlot(data=cesCoeffsData_ekl, mapping=aes(delta_1, sigma_1), facet_formula=country~nestStrParen, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta[1]), y=expression(sigma[1]))
@

<<CES_sigma_delta_graph_kle, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with (kl)e nesting.">>=
standardScatterPlot(data=subset(cesCoeffsData_kle, nestStrParen != "(iK + iL) + ()"),
                    mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta), y=expression(sigma))
@

<<CES_sigma_delta_graph_lek, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with (le)k nesting.">>=
standardScatterPlot(data=subset(cesCoeffsData_lek, nestStrParen != "(iK + iL) + ()"),
                    mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta), y=expression(sigma))
@

<<CES_sigma_delta_graph_ekl, fig.pos="H", fig.align='center', fig.width=4.5, fig.height=7, fig.cap="$\\sigma$ and $\\delta$ values for CES resample models with (ek)l nesting.">>=
standardScatterPlot(data=subset(cesCoeffsData_ekl, nestStrParen != "(iK + iL) + ()"),
                    mapping=aes(delta, sigma), facet_formula=country~nestStrParen, alpha=0.05) +
    coord_trans(y="sigma") +
    scale_x_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    scale_y_continuous(breaks=c(0, 0.5, 1.0, 2.0)) +
    labs(x=expression(delta), y=expression(sigma))
@

@@

<<CES_ternary_graph_kle, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with (kl)e nesting.">>=
standardTriPlot(data=cesCoeffsData_kle, facet_formula=country~nestStrParen)
@

<<CES_ternary_graph_lek, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with (le)k nesting.">>=
standardTriPlot(data=cesCoeffsData_lek, facet_formula=country~nestStrParen)
@

<<CES_ternary_graph_ekl, fig.pos="H", fig.align='center', fig.width=5.5, fig.height=7.5, fig.cap="$\\alpha$, $\\beta$, and $\\gamma$ values for CES resample models with (ek)l nesting.">>=
standardTriPlot(data=cesCoeffsData_ekl, facet_formula=country~nestStrParen)
@

<<CES_Spaghetti_Graph_kle, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with (kl)e nesting.">>=
cesFittedData <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", "(iK + iL) + (iQ)", "(iK + iL) + (iX)", "(iK + iL) + (iU)"))
spaghettiPlot(data=cesFittedData, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@

<<CES_Spaghetti_Graph_lek, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with (le)k nesting.">>=
cesFittedData <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", "(iL + iQ) + (iK)", "(iL + iX) + (iK)", "(iL + iU) + (iK)"))
spaghettiPlot(data=cesFittedData, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@

<<CES_Spaghetti_Graph_ekl, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=8.5, fig.cap="CES fitted models with (ek)l nesting.">>=
cesFittedData <- filter(fitted_df, model=="ces", nestStrParen %in% c("(iK + iL) + ()", "(iQ + iK) + (iL)", "(iX + iK) + (iL)", "(iU + iK) + (iL)"))
spaghettiPlot(data=cesFittedData, facet_formula=Country~nestStrParen, level=spaghettiGraphLevel) +
    labs(y="Indexed GDP (1980=1 or 1991=1)")
@

@@
